Bird beak's elaboration and exploration

### 2021-08-10 Analysis/02-MCMCglmm_mini_chains.Rmd
typos

We first ran three independent MCMC chains with the model and data described above using the consensus tree and flat priors.
We ran these models (for `§§§N_generations` sampling every `§§§N_nitt` with no burnin) until the three chains reached an effective sample size >> 200 (§§§and other diagnosis). 
<!-- % NC: I thought in MCMCglmm the nitt parameter was total number of iterations, and thin gives how often the chain is sampled? I think you've called nitt generations here but better to be consistent with MCMCglmm?
 -->
```{r, parametrise_the_model, eval = TRUE}
## Set up the parametrising chains models
param_MCMCglmm <- make.mini.chains(data         = demo_data,
                                   dimensions   = c(1:4),
                                   tree         = consensus_tree,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "clade"),
                                   residuals    = "global",
                                   priors       = 0.02,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 10000,
                                       thin   = 100,
                                       burnin = 0))

>>>>

We first ran three independent MCMC chains with the model and data described above using the consensus tree and flat priors.
We ran these models (for `§§§N_generations` sampling every `§§§N_nitt` with no burnin) until the three chains reached an effective sample size >> 200 (§§§and other diagnosis). 
<!-- % NC: I thought in MCMCglmm the nitt parameter was total number of iterations, and thin gives how often the chain is sampled? I think you've called nitt generations here but better to be consistent with MCMCglmm?
 -->

```{r, parametrise_the_model, eval = TRUE}
## Set up the parametrising chains models
param_MCMCglmm <- make.mini.chains(data         = demo_data,
                                   dimensions   = c(1:4),
                                   tree         = consensus_tree,
                                   trait.family = "gaussian",
                                   randoms      = c("global", "clade"),
                                   residuals    = "global",
                                   priors       = 0.02,
                                   verbose      = TRUE,
                                   parameters   = list(
                                       nitt   = 10000,
                                       thin   = 100,
                                       burnin = 0))

### 2021-08-10 Analysis/03-elaboration_exploration_analyses.Rmd
typos

```{r, fig.height = 10, fig.width = 10}
## Plotting it
plot.space(demo_data,
           col = colour_vector,
           levels = demo_data$clade,
           xlab = "PC1 (90.5%)",
           ylab = "PC1 (6.86%)",
           xlim = c(-2, 2),
           ylim = c(-1, 1))
points(do.call(rbind,group_centres)[,c(1,2)],
       pch = 13, col = c(colour_vector, "grey"))
plot.axes(major_axes["animal"], col = "grey",
          add = TRUE, transparent.scale = 0.01,
          centre = 0)
plot.axes(major_axes["animal:clade1"], col = colour_vector[1],
          add = TRUE, transparent.scale = 0.01,
          centre = colMeans(demo_data[demo_data$clade == "gulls", c(1,2)]))
plot.axes(major_axes["animal:clade2"], col = colour_vector[2],
          add = TRUE, transparent.scale = 0.01,
          centre = colMeans(demo_data[demo_data$clade == "plovers", c(1,2)]))
plot.axes(major_axes["animal:clade3"], col = colour_vector[3],
          add = TRUE, transparent.scale = 0.01,
          centre = colMeans(demo_data[demo_data$clade == "sandpipers", c(1,2)]))
legend("topleft",
       legend = c("phylogeny", levels(demo_data$clade)),
       col = c("grey", colour_vector),
       lty = c(1,1,1,1),
       pch = c(NA, 19, 19, 19))
```

>>>>

```{r, fig.height = 10, fig.width = 10}
## Plotting it
plot.space(demo_data,
           col = colour_vector,
           levels = demo_data$clade,
           xlab = "PC1 (90.5%)",
           ylab = "PC2 (6.86%)",
           xlim = c(-2, 2),
           ylim = c(-1, 1))
points(do.call(rbind,group_centres)[,c(1,2)],
       pch = 13, col = c(colour_vector, "grey"))
plot.axes(major_axes["animal"], col = "grey",
          add = TRUE, transparent.scale = 0.01,
          centre = 0)
plot.axes(major_axes["animal:clade1"], col = colour_vector[1],
          add = TRUE, transparent.scale = 0.01,
          centre = colMeans(demo_data[demo_data$clade == "gulls", c(1,2)]))
plot.axes(major_axes["animal:clade2"], col = colour_vector[2],
          add = TRUE, transparent.scale = 0.01,
          centre = colMeans(demo_data[demo_data$clade == "plovers", c(1,2)]))
plot.axes(major_axes["animal:clade3"], col = colour_vector[3],
          add = TRUE, transparent.scale = 0.01,
          centre = colMeans(demo_data[demo_data$clade == "sandpipers", c(1,2)]))
legend("topleft",
       legend = c("phylogeny", levels(demo_data$clade)),
       col = c("grey", colour_vector),
       lty = c(1,1,1,1),
       pch = c(NA, 19, 19, 19))
```
